\section{Stats}
The base of any RP is the stats. I wanted to cut a fine compromise between the simplicity of, say, Apocolypse World's 5: Cool, Hard, Hot, Smart, and Weird, while still getting the coverage of Mekton Zeta's 9. With that in mind, Mecha World uses the following stats:

\subsection{Cool}
With a ``Cool'' stat existing in both Apocolypse World and Mekton Zeta, it seemed silly to not include it here. Cool symbolises how a character deals with preassure. A Cool character walks out into bulletstorms fearlessly, and take the vilest insults without batting an eye. An Uncool character can most often be found cowering in fear, being reduced to tears, or not getting in the goddamn robot, Shinji.
 
\subsection{Talk}
You may walk the walk, but can you do this? Talk represents how well a character can communicate, whether that be rousing speeches, witty comebacks, or pep talks. A Talkative character can inspire the masses to their cause, humiliate opponents in battles of wits, or brief an entire squadron. An untalkative character misses key details in their explanations, accidentally insults people they're trying to inspire, or thinks of the perfect retort five days later in the shower.

\subsection{Hard}
Another stat stolen from Apocolypse World, Hard represents a character's strength and build. Can your character karate chop a pile of bricks clean in two? Do do they eat raw eggs for breakfast, and cow pie for lunch? Do they have to buy two seats at the cinema? Then they're probably a Hard character. If your character eats cup ramen three times a day, faints when struck by falling sunbeams, and doesn't know their hack squats from their hyper extensions, they probably have a low score in this stat.

\subsection{Fast}
The counterpart to Hard among the physical stats, Fast represents a character's running speed and manual dexterity. A fast character may be an Olympic athelete, a ninjutsu master, or even a world-record holding Rubik's cube solver. Slow characters have trouble getting out of bed in the morning, have trouble keeping their balance or footing, and react to dangerous situations a little too late.

\subsection{Tech}
In a darkened room, the curtains drawn, green text adorns a black background of a glowing computer screen. Such is the lifestyle of your typical Techie character. If you want to fix or augment your mecha with cool prototype weapons, hack your opponent's automated defenses to take out their base without getting out of your comfy chair, or create a GUI interface in Visual Basic to back-trace a caller's IP address, choose a high score in this stat. Non-technical characters will be relegated to padded cockpits with single buttons, lest they accidentally set off the alarms whilst trying to force a door open, or cut the wrong wire attempting to defuse a homemade bomb.

\subsection{Plan}
Have you ever walked into a room and forgotten what you came in for? Is your cockpit's monitor adorned with post-its of your various passwords? Do you often find yourself unable to react when the floor is blown out from under your feet by improvised explosive devices? If so, you probably don't have a high Plan score. Planners act fast, and they act with precision. They can make a squadron of 4 soldiers seem like a dozen to the enemy, deduce the keycode to a locked door by the pattern of grime on the keys, or reveal to their enemies that all their weaponry has been disabled from the start. They set up the dominoes, then knock them all down like a house of cards. Checkmate.
