\section{Classes}

\subsection{Operator}
{\itshape You're not like the others, are you? They all fight for something, or maybe it's more accurate to say they all still have something worth fighting for. What do you have? A klunky piece-of-shit gun, battered body armour, and a hell of a lot of history. 

How many people have you killed? Do you still remember each of their faces? Of course you fucking don't. Whatever humanity you had went out the window a long time ago. You're little more than machine now. Even the mecha are more human than you are.}

\subsubsection{Look}

Choose one for each:

Dead Eyes, Hard Eyes, or Gleeful Eyes

Military Gear, Concealing Clothes, or Casual Wear

\subsubsection{Stats}
Choose one set:
\begin{itemize}
\setlength\itemsep{0em}
\item Cool+2 Talk-2 Hard=0 Fast=0 Tech+1 Plan+2
\item Cool+2 Talk-1 Hard+1 Fast=0 Tech+1 Plan=0
\item Cool+2 Talk-1 Hard=0 Fast+1 Tech=0 Plan+1
\item Cool+2 Talk=0 Hard+1 Fast=0 Tech-1 Plan+1
\end{itemize}

\move{Volley}{target multiple enemies with a single burst}{Cool}
{Deal your damage to each enemy}
{Deal your damage to half the enemies, rounded down. The GM will tell you which ones}
{as above, but you also may hit unintended targets}

\move{Deathwish}{walk out into a storm of bullets}{Cool}
{Choose up to 3 visible enemies in range and make immediate consecutive attacks against them}
{Choose up to 3 enemies and make immediate consecutive attacks against them at the cost of taking 1-harm per target chosen}
{Make an attack against 1 enemy but receive a counterattack}

\move{Breach and Clear}{make an explosive entry into a hostile area}{Plan}
{Choose up to 3 visible enemies in range and make immediate consecutive attacks against them}
{Choose up to 2 enemies, but 1 from the following list}
{Choose one enemy and two from the list:
\begin{itemize}
\item Flying debris inflicts 1-harm with 1 piercing to you
\item There are more enemies than expected
\item You hit an unintended target
\end{itemize}}

\subsubsection{Equipment}
You have an SMG (2-harm, close, full-auto, loud, 2 weight), choose its 2 attachments:
\begin{itemize}
\item Silencer ($-$loud)
\item Skeleton Stock ($-1$ Weight)
\item AP ammo (+1 piercing)
\item Collapsible Stock (+hand)
\item IR scope (night vision)
\end{itemize}

You also have a pistol (2-harm, close, hand, semi-auto, loud, 1 weight), choose its attachment:
\begin{itemize}
\item Silencer ($-$loud)
\item .45 cal (+1-harm)
\item AP ammo (+1 piercing)
\end{itemize}

You get:
\begin{itemize}
\item Bulletproof Vest (1 armour, 1 weight)
\item 2 Stimpaks ($-1$-harm, 1 Weight)
\item 2 Explosive Kits (2 weight)
\item 3 Tactical Grenades (0 weight)
\end{itemize}

\subsubsection{Mecha Signature Weapon: Utility Rifle}
Your mecha is equipped with an assault rifle (2-harm, close, semi-auto, full-auto, loud, two-handed, 2 weight). Choose its 3 attachments:
\begin{itemize}
\item Ripper Ammo (+1-harm, messy)
\item AP Ammo (+1 piercing)
\item Dragon's Breath Ammo (fire)
\item Scope (+far)
\item Rocket Launcher (4-harm, close, far, single, loud, messy, area, +2 weight)
\item EMP Grenade Launcher (3s-harm, close, single, emp, area, +1 weight)
\item Bayonet (2-harm, 1 piercing, intimate, hand)
\end{itemize}

\movedesc{Mecha Special Ability: Possessed}{fight on despite severe wounds}{you inflict an extra 1-harm with each attack.}



\subsection{Wiseguy}
{\itshape Where would these misfits be without you, eh? Just the other day you tried to strike up a rousing conversation with the Brawler, and he \emph{hissed} at you. Hissed! Like a cat! No, no, no, these guys would be mincemeat by now if you weren't around to smooth things over.

Leave the deal-brokering, the negotiations, and the sweet-talking to you. You'll always be around to talk your way out of a sticky situation. No need to thank you, it's all part of the service. Well, unless they're armed, in which case your former friends are on their own!}
\subsubsection{Look}
Choose one for each:

Shifty Eyes, Sharp Eyes, or Gleeful Eyes

Tidy Hair, Slick Hair, or Ponytail

Concealing Clothes, Business Wear, or Snazzy Clothes

\subsubsection{Stats}
Choose one set:
\begin{itemize}
\setlength\itemsep{0em}
\item Cool+1 Talk+2 Hard-1 Fast=0 Tech=0 Plan+1
\item Cool=0 Talk+2 Hard-1 Fast+1 Tech+1 Plan=0
\item Cool-1 Talk+2 Hard-2 Fast+2 Tech+1 Plan+1
\item Cool=0 Talk+2 Hard-1 Fast-1 Tech=0 Plan+2
\end{itemize}

% written by Luke
\move{Networking}{arrive at a new location and mention an old accomplice or contact}{Talk, describe how you remember them, and recount a whacky anecdote about them}
{they're in town, and owe you a favour or their life (take +1 ongoing to interacting with them until you're even)}
{they were living here at least recently, at the GM's discretion maybe they're still here; at the very least the trail will be hot. However, things have changed since the good old days---pick 1:
\begin{itemize}
\item They've changed.
\item You've changed.
\item They don't remember you, at least not fondly.
\item You still owe them a favour or money
\end{itemize}}
{they're long gone or at the GM's discretion they're in town, but the winds of fate have positioned them to oppose you, not aid you.}

\move{Wisecrack}{tell a joke to defuse a tense situation}{Talk}
{Everyone present relaxes and becomes a little more amicable}
{Your joke falls flat, but the attempt causes everyone to calm down. Everyone becomes more amicable, but you take $-1$ forward, in shame.}
{Your light-hearted treatment of the situation pisses people off.}

\movenofail{Eye On The Door}{are in too deep and need a way out}{Plan, naming your escape route:}
{you're gone. Catch you later, suckers!}
{you can stay or go, but if you go you either leave something behind, or take something with you, the GM will tell you what.}

\subsubsection{Equipment}
You have your trusty piece(s) for when things go hot. Choose 1 and give it a nickname:
\begin{itemize}
\item Gold DE .50 AE (2-harm, 1 piercing, hand, close, semi-auto, valuable, 2 weight)
\item Dual Mini-Uzis (2-harm, two-handed, hand, close, full-auto, 1 weight) 
\end{itemize}

\subsubsection{Mecha Signature Weapon: Wave Emitter}
This unique weapon releases a beam of waves which either constructively or destructively interfere with a target mecha. When you use it, choose a target and an effect:
\begin{itemize}
\item Neutralise an EMP effect.
\item Disable or enhance their movement systems.
\item Give them $\pm 1$ ongoing.
\item Increase or decrease their damage by 1-harm.
\end{itemize}
Then roll+Plan:
\rollresnofail{The target gets the effect while you keep the weapon trained on them.}
{The effect still works, but it attracts unwanted attention, drains your own power, or resonates with other targets, affecting them as well, GM's choice.}

\move{Mecha Special Ability: Crosstalk}{listen in to the enemy's transmissions}{Talk}
{you overhear some interesting and useful information.}
{you overhear some interesting info, but it's not immediately useful.}
{you hear useless banter or the encryption is too strong. Curses!}



\subsection{Brawler}
{\itshape They always say weapons don't kill people, people do. Well, what are the weapons for, then? A weapon is nothing without a strong body wielding it. Look at the others. They think their pop-guns and glorified tree branches will protect them in a fight. Maybe, but where will they be when those weapons are taken away?

They call you names sometimes. ``Meathead'', they say. ``Numbskull'', ``Shit-For-Brains''. They laugh. Well, they'll be laughing on the other side of their faces one day. When the enemy has them jailed, and they see you removing the bars one by one like so many toothpicks. Or maybe you'll just crush one of their skulls like a watermelon. Nobody will be laughing then.}

\subsubsection{Look}
Choose one for each:

Wild Eyes, Determined Eyes, or Bored Eyes

Shorn Hair, Wild Hair, or Mask

Sporty Gear, Outdoor Gear, or Remnants of Experimentation

\subsubsection{Stats}
Choose one set:
\begin{itemize}
\setlength\itemsep{0em}
\item Cool+2 Talk=0 Hard+2 Fast+1 Tech-2 Plan=0
\item Cool+1 Talk+1 Hard+2 Fast+1 Tech-1 Plan-1
\item Cool-1 Talk-1 Hard+2 Fast+2 Tech+1 Plan-1
\item Cool+1 Talk+1 Hard+2 Fast+1 Tech+1 Plan-2
\end{itemize}

\subsubsection{My Guns Are Right Here}
Your unarmed strike counts as a weapon: (2-harm, two-handed, intimate, fused, 0 weight).

\movedesc{Full Force}{succeed a Brawl with a 10+}{you may choose both options.}

\move{Imagine This Is Your Head}{intimidate information out of an enemy with a show of force}{Hard}
{they immediately tell you what you want to know. What you do next is up to you.}
{they agree to tell if you let them go, and want to be certain they won't be harmed.}
{they spit in your face, to the extent possible.}

\movedesc{It's a Monster!}{stand your ground}{you may roll Hold Fast with Hard instead of Cool}

\subsubsection{Equipment}
You have your fists, but I guess you can also have a gun, you know, just to be on the safe side. Choose one:
\begin{itemize}
\item Hunting Shotgun (3-harm, semi-auto, loud, messy, close, 2 weight)
\item Grenade Launcher (4-harm, semi-auto, loud, messy, close, area, 3 weight)
\item Rocket Launcher (4-harm, single, loud, messy, close, far, area, 3 weight)
\end{itemize}

You get:
\begin{itemize}
\item 2 Stimpaks ($-2$-harm, 1 weight)
\end{itemize}

\subsubsection{Mecha Signature Weapon: Reaper}
Your mecha is equipped with a melee weapon: (2-harm, intimate, fused, 0 weight). Its look is up to you.
Every time you destroy a mecha, add one of the following attachments:
\begin{itemize}
\item Hard Scrap (+1 harm)
\item Sharp Scrap (+1 harm)
\item Power Cutter (+1 piercing, messy)
\item Long Scrap (+hand)
\item Flexible Scrap (+versatile)
\item Ingited Fuel (+fire)
\end{itemize}
The attachments are lost once you exit combat, GM's call.

\move{Mecha Special Ability: Overclock}{pull all the power you can from your mecha's core}{Hard}
{hold 3}{hold 1}{the failed attempt causes you to take -1 forward}
Spend your hold when you take a hit to immediately counterattack. If the attacker is within close range, you immediately close the distance. Take -1 forward when you spend your last hold in this way. At any time you can release all your hold for no penalty.



\subsection{Swordsmaster}
{\itshape These fools lack honour and discipline. Look at them now, laughing carelessly over a shared lunch. They could be attacked right this minute, and only you would be able to defend yourself. While they waste away their time you sit here, tirelessly drawing and resheathing your sword to shave off those precious milliseconds that could mean the difference between life and death.

A warrior's life is tough, to be sure, but it has its rewards. What are they to you? To lay down your life in defense of your lord, like the samurai of old? Or do you prefer to feel the breath of your enemy leave them, while you bask in the knowledge that when it came right down to it, you were better than them? Whatever your goal, you will find it hard to attain with these weaklings around. They lack honour and discipline, yes, but you can change that.}

\subsubsection{Look}

Choose one for each:

Tired Eyes, Fierce Eyes, or Piercing Eyes.

Topknot, Wild Hair, or Shorn Hair

Gi and Hakama, Noble Wear, or Bandages

\subsubsection{Stats}
Choose one set:
\begin{itemize}
\setlength\itemsep{0em}
\item Cool+1 Talk-1 Hard+1 Fast+2 Tech-1 Plan+1
\item Cool+1 Talk+1 Hard+1 Fast+2 Tech-1 Plan-1
\item Cool=0 Talk-1 Hard+2 Fast+2 Tech-1 Plan-1
\item Cool+1 Talk-1 Hard=0 Fast+2 Tech+1 Plan=0
\end{itemize}

\subsubsection{Signature Weapon}
You are the bone of your sword. Perhaps it was created by a master smith centuries ago, or perhaps you found it on the floor. Regardless, this is your sword and it is irreplaceable, so don't lose it.

Your base sword comes with a matching sheath and is (2-harm, hand, 2 weight).

Choose a look:
\begin{itemize}
\item Straight or Curved
\item Single-edged, Double-edged, or Thrusting
\item Simple Design, Elaborate Design, or High-Tech Design
\end{itemize}

Choose two enhancements:
\begin{itemize}
\item Serrated (+1-harm)
\item Vibrating (+1 piercing, messy, hi-tech)
\item Disposable (infinite)
\item Perfectly-Balanced (precise)
\item Tasseled (+short, thrown)
\item Well-Crafted ($-1$ weight)
\item Twin (you have two and can dual-wield, but each individually is 1-harm and 1 weight. You can deal damage with both during an attack, but your other enhancement applies to only one blade)
\end{itemize}

\move{Quickdraw}{are attacked in melee by an enemy while your sword is sheathed}{Fast}
{draw your sword and inflict your damage, negating the incoming attack}
{draw your sword and inflict your damage, but the enemy's attack still lands}
{the enemy reaches you before you can draw your sword}

\movenofail{You Are Already Dead}{resheathe your sword immediately after dealing damage}{Cool}
{Choose 2:
\begin{itemize}
\item Additional wounds are revealed on your enemy, adding 1-harm to the damage and applying the messy tag.
\item Your spirit overflows, hitting nearby enemies for 1s-harm
\item A nearby mook flees in terror
\item A nearby character is impressed
\end{itemize}}
{choose 1}

\subsubsection{Equipment}
You get your signature weapon, but choose your defenses:
\begin{itemize}
\item Padded Clothes (1-armour, 1 weight)
\item Samurai Armour (2-armour, 3 weight)
\item Exoskeleton (2-armour, fused, 0 weight)
\end{itemize}

\subsubsection{Mecha Signature Weapon: Raikiri}
Your mecha's sword Raikiri (2-harm, hand, 2 weight) is as fast as lightning. When you \textbf{cut an enemy with Raikiri}, roll+Fast.
\rollresnofail{electricity flows out of the cut, striking other nearby enemies for 1s-harm and temporarily stunning them with an EMP}
{the electricity inflicts 1s-harm to other nearby enemies}

\move{Mecha Special Ability: Harakiri Blade}{commit seppuku with Raikiri}{Cool}
{Raikiri begins to glow with an unnatural light. Choose 2 enhancements from the list below.}
{Choose 1 enhancement. At your option you can choose 2 but take 1-harm.}
{You just stabbed yourself. Well done. Take 1-harm.}
Enhancements:
\begin{itemize}
\item +1-harm
\item +1 forward
\item (+fire)
\item (+close)
\end{itemize}
The enhancements wear off when you sheathe your sword or exit combat, GM's call.



\subsection{Hikikomori}
{\itshape What was that noise? Is someone there? Maybe if you're quiet enough, they'll think you're not in. You shun outside contact. Friends only ever let you down. To support yourself, here, with your own two hands is enough. Well, in addition to the food your nice older sibling leaves outside your door.

The gentle hum of the machinery, the moonlight streaming in through the viewing port. This is the life. Solitude is not loneliness; that's what the others don't understand. Always asking what's wrong. They'll never understand you. Not like you do.}

\subsubsection{Look}
Choose one for each:

Tired Eyes, Calculating Eyes, or Hair Over Eyes.

Messy Hair, Long Straight Hair, or Covered Hair

Tracksuit, T-shirt and Jeans, or Pyjamas

\subsubsection{Stats}
Choose one set:
\begin{itemize}
\setlength\itemsep{0em}
\item Cool+1 Talk-2 Hard-1 Fast+1 Tech+2 Plan+2
\item Cool-1 Talk+1 Hard=0 Fast=0 Tech+2 Plan+1
\item Cool+1 Talk-1 Hard+2 Fast-1 Tech+2 Plan-1
\item Cool=0 Talk=0 Hard-2 Fast+2 Tech+2 Plan+1
\end{itemize}

\move{Security Expert}{attempt to overcome network security}{Tech}
{choose three from the list below:
\begin{itemize}
\item You learn something new about your adversary
\item You disable something of the enemy's
\item You sow misinformation among the enemy
\item Your intrusion is undetected
\end{itemize}}
{choose one}
{you are detected before you can do anything}

\move{Don't Come In!}{trap a room or entrance}{Plan and deplete 1 Tech Item}
{hold 3}
{hold 2}
{hold 1, plus whatever the GM says when you spend it}
Spend your hold when a character approaches the trap to choose one of the following:
\begin{itemize}
\item neutralise the intruder
\item observe the intruder
\item play a prerecorded message to the intruder
\end{itemize}

\movedesc{Kindred Spirits}{talk with another weirdo}{invert your talk score when rolling +Talk with them}

\subsubsection{Equipment}
Choose a weapon:
\begin{itemize}
\item Antique sword (hand, valuable, 2-harm, 2 weight)
\item Taser (intimate, 2s-harm, hi-tech, 0 weight)
\end{itemize}

You get:
\begin{itemize}
\item 2 Tech Items (hi-tech, 1 weight)
\item Laptop (valuable, hi-tech, 1 weight)
\item An item which affords you emotional security, at your option it can also provide 1-armour
\end{itemize}

\subsubsection{Mecha Signature Weapon: Violation}
Your mecha is equipped with a melee weapon (2-harm, hand, 2 weight). Its look is up to you.

When you \textbf{deal damage with Violation}, Roll+Tech:
\rollresnofail{the target, if it survives, is under your control. You can control the mecha as though it were piloted by a hireling of yours. The actual pilot is locked out of the system.}
{you gain partial control. You can control either the movement systems, the weaponry, or another prominent system of your choice.}
You can only control one target at a time. If you take a new thrall, you lose control over the previous one.

\subsubsection{Mecha Special Ability: No Words}
Your mecha is equiped with the latest jamming technology. Any signals originating, terminating, or passing through the area within close range of your mecha can be jammed, making them corrupted and unrecognisable. However, participants will know they are being jammed.



\subsection{Assassin}
{\itshape For what reason do you do this? Don't bother lying to me, everyone has a reason. People may fight trivially, but they always kill for a cause. Be that a higher power or ideology, the sweet taste of revenge, or just the undeniable allure of filthy lucre.

You have as myriad methods of killing as you have targets. The partygoing billionaire may warrant a .50 cal bullet to the brain from the roof of an adjacent building, but the paranoid mob boss will require a more\ldots intimate approach. Do you feel pleasure as the garotte denies vital oxygen to his lungs? Did this man bring untold suffering to countless innocents? Or was he just on the wrong side of a million-dollar transaction?}

\subsubsection{Look}
Choose one for each:

Dead Eyes, Calculating Eyes, or Hard Eyes.

Shorn Hair, Slick Hair, or Hooded

Fatigues, Formal Wear, or Concealing Wear

\subsubsection{Stats}
Choose one set:
\begin{itemize}
\setlength\itemsep{0em}
\item Cool+1 Talk=0 Hard+1 Fast=0 Tech-1 Plan+2
\item Cool=0 Talk+1 Hard=0 Fast+1 Tech-1 Plan+2
\item Cool+1 Talk-2 Hard-1 Fast+2 Tech+1 Plan+2
\item Cool+2 Talk-1 Hard-1 Fast-1 Tech+1 Plan+2
\end{itemize}

\move{Assassinate}{try to take down a target with a high-powered rifle}{Plan}
{you take out your target without leaving evidence. At your option you can also make it look like an accident}
{Choose one:
\begin{itemize}
\item you take out your target but leave behind evidence
\item your target is permanently crippled in some way, but lives. However, you do not leave behind evidence
\end{itemize}}
{your target is only permanently crippled, and you leave evidence}

\move{Selective Hearing}{attempt to pick out a target in a crowd that you're in}{Cool and say what you're listening out for}
{you identify your target and also overhear some interesting information}
{you identify your target, but they're just leaving}
{you narrow your target to one of three people, all of whom are heading in different directions}

\movedesc{Silent Takedown}{catch an enemy unawares or have an enemy defenseless}{you can kill them without a sound, you don't need to use a weapon. Snap their neck if you have to.}

\subsubsection{Equipment}

You have your trusty sniper rifle (3-harm, far, single, loud, hi-tech, 2 weight). Choose 2 attachments:
\begin{itemize}
\item Silencer ($-$loud)
\item ACOG scope (+close)
\item .50 cal ammo (ignores armour, messy)
\item Bipod (+distant)
\item Magazine feed ($-$single, +semi-auto)
\end{itemize}

You also pick one of the following sidearms:
\begin{itemize}
\item Silenced 9mm (2-harm, hand, close, semi-auto, 1 weight)
\item Sawn-off Shotgun (3-harm, close, loud, 2 weight)
\end{itemize}

You get:
\begin{itemize}
\item Butterfly knife (3-harm, intimate, 0 weight)
\item Garrote wire
\item Leather gloves
\item 1 Explosives Kit (1 weight)
\end{itemize}

\subsubsection{Mecha Signature Weapon: Osiris Cannon}
Part of your mecha is in fact a high-powered stabilised projectile launcher. (3-harm, single, far, distant, loud, messy, fused, 3 weight) Describe its look and where it is attached.

When you \textbf{land a hit with the Osiris Cannon}, you can choose to trade harm for the destruction of the target's equipped mecha items, at the rate of 1-harm for 2 items destroyed.

\movedesc{Mecha Special Ability: Disguise}{examine the remains of a destroyed mecha}{you can tune your IFF signal to match. Any automated systems will react as though you were the mecha in question. However, this does nothing to change your outward appearance.} 



\subsection{Techie}
{\itshape You know what Mecha World is about: Mecha. Big mecha, small mecha, mecha with big, fuck-off guns, or mecha with clouds of auto-repairing nanomachines. In the end it all comes down to who has the better mecha, and your mecha are the best of the best.

So you'll toil away in your workshop, wheeling out your subatomic particle accelerator cannons, or your anti-trojan quantum-encrypted datapath subnets. You just wish you would get a better reaction than a blank stare when you try to explain how they work.}

\subsubsection{Look}

Caring Eyes, Tired Eyes, or Thick Glasses

Messy Hair, Tied Hair, or Shorn Hair

Work Gear, Hazmat Gear, or Researcher Wear

\subsubsection{Stats}
Choose one set:
\begin{itemize}
\setlength\itemsep{0em}
\item Cool=0 Talk-1 Hard+1 Fast=0 Tech+2 Plan+1
\item Cool+1 Talk-2 Hard+2 Fast=0 Tech+2 Plan=0
\item Cool=0 Talk-1 Hard=0 Fast-1 Tech+2 Plan+2
\item Cool-1 Talk=0 Hard+1 Fast+1 Tech+2 Plan=0
\end{itemize}

\movedesc{Prototype}{draw up designs for a new mecha weapon or subsystem}{describe what it does. Prototypes are always possible, but the GM will impose 1 to 4 of the following restrictions:}
\begin{itemize}
\item It's going to take time.
\item It will only work under certain circumstances.
\item You'll need the help of someone, the GM will say who.
\item It's going to cost a lot of money.
\item The best you can do is a less powerful or reliable version.
\item You’ll have to deconstruct something for the parts, the GM will say what.
\end{itemize}

% written by Luke
\move{It's Like Putting Too Much Air In A Balloon!}{attempt to solve a technical conundrum}{Tech}
{the solution is clear as day to you, but now you may have to explain it to the others. (The GM will tell you the solution, it's up to you to technobabble)}
{as above, but there's a catch---and ye cannae bend the laws of physics. Choose one and don't forget to technobabble:
\begin{itemize}
\item It's going to take time.
\item You’ll have to deconstruct something for the parts, the GM will say what.
\item You put yourself in danger.
\end{itemize}}
{your technobabble confuses and alienates those present. Take $-1$ forward to social interactions with them.}

\movedesc{Lug}{make a move whilst encumbered}{instead of making the Encumbrance move, you may throw at least 1 weight (at an enemy, to a safe location etc), and roll without penalty.}

\subsubsection{Equipment}
Choose your weapon:
\begin{itemize}
\item Plasma Cutter (3-harm, 1 piercing, two-handed, hand, hi-tech, 3 weight)
\item 2 Spanners (2-harm, intimate, hand, close, thrown, 1 weight)
\item Nail Gun (2-harm, 1 piercing, semi-auto, close, 2 weight)
\end{itemize}

Choose your defenses:
\begin{itemize}
\item Kevlar Vest (1 armour, 1 weight) and 2 Tech Items (hi-tech, 1 weight)
\item Full Plate (2 armour, 3 weight)
\end{itemize}

\subsubsection{Mecha Signature Weapon: Compensator}
The Compensator is a melee weapon (2-harm, hand, 2 weight). Describe its look.
When you inflict damage with the Compensator, gain 1 balance. You can spend balance to restore a depleted Defensive Measure to a nearby ally.

\move{Mecha Special Ability: Grey Goo}{release a cloud of nanomachines}{Tech}
{The cloud gets to work, dismantling enemy mecha and repairing friendly ones.}
{The cloud only has enough processing power to handle one task, repair or destuction. Choose which one.}
{Most of the cloud malfunction and self-destruct, but a small portion go haywire, repairing enemies and dismantling allies.}

%\subsection{Class Name}
%{\itshape}
%\subsubsection{Look}
%\subsubsection{Stats}
%Choose one set:
%\begin{itemize}
%\setlength\itemsep{0em}
%\item Cool=0 Talk=0 Hard=0 Fast=0 Tech=0 Plan=0
%\item Cool=0 Talk=0 Hard=0 Fast=0 Tech=0 Plan=0
%\item Cool=0 Talk=0 Hard=0 Fast=0 Tech=0 Plan=0
%\item Cool=0 Talk=0 Hard=0 Fast=0 Tech=0 Plan=0
%\end{itemize}
%\subsubsection{Equipment}