\section{Mecha}

It wouldn't be Mecha World without mecha: the giant robots our heroes use to fight the bad guys---usually in weaker mecha.

Each class has their own unique mecha weapon and ability, but it's up to the group to decide how these are realised. Has each character had their mecha custom-built for them, or did the party come across them recently, conveniently geared up to match their strengths?

The stats of the mecha themselves reflect the strengths and weaknesses of their pilots, meaning rolls whilst in the mecha use the pilot's stats; even when it wouldn't seem to make sense. You might think, why does it matter how strong the pilot is when he's controlling fifty tonnes of hydraulics? This again can can be reflected in the fiction. Perhaps the mecha have to be closely tuned to the capabilities of the pilot for optimal compatibility, or maybe the mecha are literally powered by the will or energy of the pilots themselves. (Think Spiral Power)

%Mecha are generally humanoid; they have a head, torso, two arms, and two legs. But here the visual similarities between them end. 

\subsection{Mecha Items}
Okay, so you have your mecha and its weapon, but the mecha's load capacity is much higher than that, right? The mecha has the same max load as the pilot, with a few important distinctions.

First off, they're clearly not in the same units. Giant robots can carry objects orders of magnitude heavier than people can. So people can't carry mecha-sized items, and mecha can trivially carry any number of human-sized items, within reason.

Secondly, whilst humans can overexert themselves to carry more then their max load (invoking the Encumbrance move), mecha are a bit more concrete in their abilities. Mecha can not usually carry above their max load.

But don't start calculating how many valuable relics or moon-rocks you can fill up on just yet. You're going to need all the surplus load you can get for Mecha Items. Your mecha's Mecha Items are chosen at character generation. When you stop for repairs, you can replenish your depleted Mecha Items, as well as optionally choose one to replace with a different type. Depleted or shed Mecha Items also weigh nothing, so you can free up space for all those oversized baubles your pilots can't carry.

The available Mecha Items (all 1 weight) are:

\paragraph{Defensive Measures:}
These are things like ablative shielding or anti-lock-on flares: passive items which prevent an attack from dealing damage. When you take damage, you can deplete as many of this item as you want to prevent harm 1-for-1.

\paragraph{Guided Missiles:}
Rather than being a separate weapon, mecha in Mecha World just have racks upon racks of HE missiles or similar packed into them. This item represents one salvo, which can be fired-and-forgotten to seek out the nearest enemy and deal 1-harm to them---provided, of course, that they don't evade the attempt with a Defensive Measure or some other ability.

\paragraph{Impulse Thrusters:}
These rockets expel a sizeable portion of propellant incredibly fast, exerting a considerable force that can be used to propel your mecha in a given direction, or other things away from you, depending on how hard you hold on to the ground. Unfortunately, their warm-up time makes them unsuitable for use in evasive manoeuvres.