% Operator Inspirations: Venom Snake, Jules, Price

\subsection{Veteran}
{\itshape You're not like the others, are you? They all fight for
  something, or maybe it's more accurate to say they all still have
  something worth fighting for. What do you have? A klunky
  piece-of-shit gun, battered body armour, and a hell of a lot of
  history.

How many people have you killed? Do you still remember each of their
faces? Of course you fucking don't. Whatever humanity you had went out
the window a long time ago. You're little more than machine now. Even
the mecha are more human than you are.}

\subsubsection{Look}

Choose one for each:

Dead Eyes, Hard Eyes, or Bored Eyes

Military Gear, Concealing Clothes, or Casual Wear

\subsubsection{Stats}
Choose one set:
\begin{itemize}
\setlength\itemsep{0em}
\item Cool$+2$ Talk$-2$ Hard${=}0$ Fast${=}0$ Tech$+1$ Plan$+2$
\item Cool$+2$ Talk$-1$ Hard$+1$ Fast${=}0$ Tech$+1$ Plan${=}0$
\item Cool$+2$ Talk$-1$ Hard${=}0$ Fast$+1$ Tech${=}0$ Plan$+1$
\item Cool$+2$ Talk${=}0$ Hard$+1$ Fast${=}0$ Tech$-1$ Plan$+1$
\end{itemize}

Your Max Health and Max Load are both 8+Hard.

\subsubsection{Philosophy}
Choose one:
\paragraph{Yin:} Cause a massacre.
\paragraph{Yang:} Open up to somebody.

\subsubsection{Introductions}
At the start of the first session, or when a new character joins, go round for introductions.
When you introduce your character, answer the following questions out loud:
\begin{itemize}
\item What do you look like? What impression does that give?
\item What do people think you're like? What about after they talk to you for five minutes?
\item In what way is people's first impression of you wrong or not quite the full story?
\end{itemize}

Then ask at least one of the following of the other characters:
\begin{itemize}
\item "Which one of you knew me before I lost my humanity?" Whoever answers, offer that player $+1$-interest.
\item "Which one of you has seen me at my worst?" Whoever answers, offer that player $-1$-interest.
\end{itemize}
Tell the others 0-interest.

After each other character's introduction:
\begin{itemize}
\item You try not to get too attached. Your interest in them is 1 less than whatever they offer you.
\end{itemize}

\subsubsection{Starting Moves}
You start with four moves from the ones below:

% You *can* leave options which would imply an unintended target is hit, like the first choice in Burst
\subsubsection{Trigger Discipline} You never hit unintended targets with a weapon. You cannot pick options that explicitly cause this to happen, and if a move tells you that you hit unintended targets, ignore it.

\move{Deathwish}{walk out into a storm of bullets}{Cool}
{Deal damage to all visible targets in range.}
{Choose a number of visible targets in range. Deal your damage to them, then take that many harm.}

\move{Breach and Clear}{make an explosive entry into a hostile area}{Plan}
{Deal damage to all visible targets in range.}
{as 10+, but there was something unexpected on the other side. The GM will tell you what.}

\subsubsection{Stone Cold} You never have to \linkmove{Persevere} to shoot someone, no matter how high the stakes.

\subsubsection{Did I Break Your Concentration?} Shooting someone or one of their associates always counts as holding up your end of a \linkmove{Bargain} with them.

\movedesc{Battlefield Instincts}{leap into battle, figuring things out as you go}{you may perform \linkmove{Situational Analysis} as though you rolled a 7--9 on the move.}

\subsubsection{Equipment}
You have an SMG (2-harm, close, full-auto, loud, 2 weight), choose 2 customisations:
\begin{itemize}
\item Silencer ($-$loud)
\item Skeleton Stock ($-1$ Weight)
\item AP Ammo ($+1$ piercing)
\item Collapsible Stock (+hand)
\item IR Scope (night vision)
\end{itemize}

You also have a pistol (2-harm, close, hand, semi-auto, loud, 1 weight), choose a customisation:
\begin{itemize}
\item Silencer ($-$loud)
\item Revolver Action ($+1$-harm, single)
\item AP ammo ($+1$ piercing)
\end{itemize}

You get:
\begin{itemize}
\item Bulletproof Vest (1 armour, 1 weight)
\item 2 Stimpaks (0 Weight)
\item 2 Explosive Kits (2 weight)
\item 3 Tactical Grenades (0 weight)
\end{itemize}

\subsubsection{Improvement}
\begin{itemize}
\item get $+1$ Cool (max $+3$)
\item get $+1$ Talk (max $+2$)
\item get $+1$ Hard (max $+2$)
\item get $+1$ Fast (max $+2$)
\item get $+1$ Tech (max $+2$)
\item get $+1$ Plan (max $+2$)
\item get a new Operator move
\item get a new Operator move
\item get an Agency, \linkmove{Mission}, and \linkmove{Call For Support}
\item get a Bodyguard and \linkmove{Command}
\end{itemize}