% Spy Inspiration: James Bond, Black Widow, Solid Snake
\subsection{Spy}

{\itshape Cast your eyes around at the others. Do they suspect your
  true motivation? Would they still treat you the same if they knew?
  If they knew of your midnight rendezvouses or your encrypted calls;
  if they knew of your mission, if they knew what you'd done, what
  would they think?

You look into their unsuspecting eyes, you laugh at their jokes, and
then you lie to their faces. Do you applaud their successes? Do you
cheer for their good fortune? When they die, do you shed tears? For
you, the mission is paramount. Are your companions any more than
simply a means to that end?}

\subsubsection{Look}
Choose one for each:

Bored Eyes, Determined Eyes, or Shifty Eyes.

Neat Hair, Slick Hair, or Extravagant Hair

Concealing Clothes, Revealing Clothes, or Formal Wear.

\subsubsection{Stats}
Choose one set:
\begin{itemize}
\setlength\itemsep{0em}
\item Cool$-1$ Talk$+2$ Hard$-1$ Fast$-1$ Tech$+1$ Plan$+2$
\item Cool$+1$ Talk$+2$ Hard${=}0$ Fast$-2$ Tech$+2$ Plan${=}0$
\item Cool$+1$ Talk$+2$ Hard$-1$ Fast${=}0$ Tech${=}0$ Plan$+1$
\item Cool$+1$ Talk$+2$ Hard$+1$ Fast$-1$ Tech$+1$ Plan$-1$
\end{itemize}

Your Max Health and Max Load are both 6+Hard.

\subsubsection{Philosophy}
Choose one:
\paragraph{Yin:} Decieve somebody.
\paragraph{Yang:} Share information with the party.

\subsubsection{Introductions}
At the start of the first session, or when a new character joins, go round for introductions.
When you introduce your character, answer the following questions out loud:
\begin{itemize}
\item What do you look like? What impression does that give?
\item What do people think you're like? What about after they talk to you for five minutes?
\item In what way is people's first impression of you wrong or not quite the full story?
\end{itemize}

Then ask at least one of the following of the other characters:
\begin{itemize}
\item "Which one of you is my accomplice?" Whoever answers, offer that player 1-interest.
\end{itemize}
Tell the others $-1$-interest. You can't risk people finding out about you.

After each other character's introduction:
\begin{itemize}
\item You're a good judge of character. Your interest in them is up to 1 different to whatever they offer you, your call.
\end{itemize}

\subsubsection{Starting Moves}
You start with \linkmove{Agency}, \linkmove{Mission}, and \linkmove{Call For Support}. Choose one more move from the others below:

\subsubsection{Agency}\label{sec:Agency}
You take your orders from a shadowy government or private agency.

Choose your Agency's field:
\begin{itemize}
\item Security (task: to protect interests)
\item Environmentalism (task: to purify)
\item Public Relations (task: to (mis)inform)
\item Corporate (task: to profit)
\item Journalism (task: to blackmail)
\end{itemize}

Choose 2 strengths and 1 weakness from the list below:
\begin{itemize}
\item Influence (influential\slash ignored)
\item Money (wealthy\slash underfunded)
\item Force (militaristic\slash pacifistic)
\item Knowledge (omniscient\slash naive)
\end{itemize}

The Agency requires you to keep the fact you work for them a secret. At the end of each session,
ask the following of each player whose character is not an accomplice.
The GM picks an NPC and answers once on their behalf, and is never an accomplice.

``Does your character know my true nature?''

If a player answers ``Yes'', and explains how they found out, they mark experience and become an accomplice.

For each ``No'' response, mark experience.

\subsubsection{Mission}\label{sec:Mission}
The Agency has given you a mission. Choose its objective:
\begin{itemize}
\item Destroy or kill \_\_\_. (disaster: they get too powerful)
\item Obtain or steal \_\_\_. (disaster: it falls into the wrong hands)
\item Protect \_\_\_ from attackers or kidnappers. (disaster: they're gone)
\item Discover the truth about \_\_\_. (disaster: the case is frozen)
\end{itemize}

At the start of each session, the GM will give you a task to complete relating to the mission:

If you complete it, get 3 \money , or 4 \money if it lead to the success of the mission. If you fail to complete it by the session end, mark one slip-up. Three slip-ups means disaster strikes.

When the mission is completed, mark experience and choose a new mission.

\movedesc{Call For Support}{contact the Agency to request assistance}{
tell the GM what you want to achieve. The Agency will always give you support, but the GM
will choose up to two from the following list, up to one if the request is covered by one of the Agency's
strengths, or up to three if it is covered by their weakness.
\begin{itemize}
\item It'll take time.
\item It's not quite what you asked for.
\item It'll cost you.
\item First you'll need to \_\_\_.
\end{itemize}}

\move{Gadgets}{reveal a mundane item in your possession to be a hidden gadget}{Tech}{it's just what you needed. Treat the mundane item as a Tech Item or single-use knockout weapon.}{it works, but choose one:
  \begin{itemize}
  \item It's been damaged and is less effective.
  \item It has an unexpected side-effect.
  \item It's only effective under a certain condition, the GM will say what needs to be done.
  \end{itemize}
}

\subsubsection{Concealed Carry}
No level of examination will ever reveal any items you are hiding on your person.

\movedesc{Pathological Liar}{bend the truth, tell a white lie, or provide alternative facts}{take +1 forward.}

\subsubsection{Equipment}
You get:
\begin{itemize}
\item Silenced 9mm (2-harm, hand, close, semi-auto, 1 weight)
\end{itemize}

\subsubsection{Improvement}
\begin{itemize}
\item get $+1$ Cool (max $+2$)
\item get $+1$ Talk (max $+3$)
\item get $+1$ Hard (max $+2$)
\item get $+1$ Fast (max $+2$)
\item get $+1$ Tech (max $+2$)
\item get $+1$ Plan (max $+2$)
\item get a new Spy move
\item get a new Spy move
\item get a move from any class
\item get a move from any class
\end{itemize}