% Techie Inspiration: Scotty, AW Savvyhead, TF2 Engineer
\subsection{Techie}
{\itshape You know what Mecha World is about: Mecha. Big mecha, small
  mecha, mecha with big, fuck-off guns, or mecha with clouds of
  auto-repairing nanomachines. In the end it all comes down to who has
  the better mecha, and your mecha are the best of the best.

So you'll toil away in your workshop, wheeling out your subatomic
particle accelerator cannons, or your anti-trojan quantum-encrypted
datapath subnets. You just wish you would get a better reaction than a
blank stare when you try to explain how they work.}

\subsubsection{Look}

Caring Eyes, Tired Eyes, or Thick Glasses

Messy Hair, Tied Hair, or Shorn Hair

Work Gear, Hazmat Gear, or Researcher Wear

\subsubsection{Stats}
Choose one set:
\begin{itemize}
\setlength\itemsep{0em}
\item Cool${=}0$ Talk$-1$ Hard$+1$ Fast${=}0$ Tech$+2$ Plan$+1$
\item Cool$+1$ Talk$-2$ Hard$+2$ Fast${=}0$ Tech$+2$ Plan${=}0$
\item Cool${=}0$ Talk$-1$ Hard${=}0$ Fast$-1$ Tech$+2$ Plan$+2$
\item Cool$-1$ Talk${=}0$ Hard$+1$ Fast$+1$ Tech$+2$ Plan${=}0$
\end{itemize}

Your Max Health and Max Load are both 6+Hard.

\subsubsection{Philosophy}
Choose one:
\paragraph{Yin:} Kill someone in an unorthadox way.
\paragraph{Yang:} Repair something.

\subsubsection{Introductions}
At the start of the first session, or when a new character joins, go round for introductions.
When you introduce your character, answer the following questions out loud:
\begin{itemize}
\item What do you look like? What impression does that give?
\item What do people think you're like? What about after they talk to you for five minutes?
\item In what way is people's first impression of you wrong or not quite the full story?
\end{itemize}

Then ask at least one of the following of the other characters:
\begin{itemize}
\item "Which one of you has commissioned my services for a project?" Whoever answers, offer that player 1-interest.
\end{itemize}
Tell the others $-1$-interest. You tend to alienate others.

After each other character's introduction:
\begin{itemize}
\item Choose one and tell them "I think you're the most intelligent." Your interest in them is 1 more than whatever they offer you.
\item Choose one and tell them "I figure you for the biggest potential problem." Your interest in them is 1 more than whatever they offer you.
\item You’ve got other stuff to do and other stuff to learn. Your interest in the others is 1 less than whatever they offer you.
\end{itemize}

\subsubsection{Starting Moves}
You start with four moves from the ones below:

\subsubsection{Technical Specialty}\label{sec:Technical Specialty}
Choose an area of expertise:
\begin{itemize}
\item Pharmacology and Virology
\item Physics and Metaphysics
\item Computer Science and Cryptography
\item Engine Mechanics and Ballistics
\item Aeronautics and Astronautics
\end{itemize}
When you first encounter an important phenomenon (your call) covered by your area of expertise you can ask the GM any one question about it; the GM will answer truthfully. The GM may then ask you where you learned of or previously encountered the phenomenon.

\movedesc{Prototype}{have time and a supply of materials}{you may draw up designs for a new technological marvel. Describe what it does to the GM. Prototypes are always possible, but the GM may impose one or more of the following restrictions:}
\begin{itemize}
\item It's going to take time.
\item It will only work under certain circumstances.
\item You'll need the help of someone, the GM will say who.
\item It's going to cost you.
\item The best you can do is a less powerful or reliable version.
\item You’ll have to deconstruct something for the parts, the GM will say what.
\end{itemize}

% written by Luke
\move{It's Like Putting Too Much Air In A Balloon!}{attempt to solve a technical conundrum}{Tech}
{the solution is clear as day to you, but now you may have to explain it to the others. (The GM will tell you the solution, it's up to you to technobabble)}
{as above, but there's a catch---and ye cannae bend the laws of physics. Choose one and don't forget to technobabble:
\begin{itemize}
\item It's going to take time.
\item You’ll have to deconstruct something for the parts, the GM will say what.
\item You put yourself in danger.
\end{itemize}}

% maybe getting rid of weight
\movedesc{Lug}{make a move whilst encumbered}{instead of making the Encumbrance move, you may throw at least 1 weight (at an enemy, to a safe location etc), and roll without penalty.}

\subsubsection{Man's Better Friend}
You have a mechanical companion. It cannot fight, but it moves autonomously and follows complex orders, can record and produce sound, and can pick up and carry appropriately sized objects. Choose two extra abilities:
\begin{itemize}
\item It can turn invisible.
\item It can fly.
\item It can record video.
\item You can access its feeds remotely.
\item It can help you fight. When you \linkmove{Brawl}, take +1 to your roll.
\item It can release an electical shock to stun anyone touching its metal frame. (2s-harm, fused, intimate)
\end{itemize}

\move{Jury Rig}{use a piece of equipment for something other than its intended purpose}{Tech}
{choose one:}
{choose one, and the GM chooses one:
\begin{itemize}
\item The equipment fails in its primary purpose.
\item The equipment is damaged beyond repair.
\item A previously-unknown function of the equipment is revealed.
\item The equipment reacts dangerously.
\end{itemize}}

\subsubsection{Equipment}
Choose your weapon:
\begin{itemize}
\item Plasma Cutter (3-harm, 1 piercing, two-handed, hand, hi-tech, 3 weight)
\item 2 Spanners (2-harm, intimate, hand, close, thrown, 1 weight)
\item Nail Gun (2-harm, 1 piercing, semi-auto, close, 2 weight)
\end{itemize}

Choose your defenses:
\begin{itemize}
\item Kevlar Vest (1 armour, 1 weight) and 2 Tech Items (hi-tech, 1 weight)
\item Full Plate (2 armour, 3 weight)
\end{itemize}

\subsubsection{Improvement}
\begin{itemize}
\item get $+1$ Cool (max $+2$)
\item get $+1$ Talk (max $+2$)
\item get $+1$ Hard (max $+2$)
\item get $+1$ Fast (max $+2$)
\item get $+1$ Tech (max $+3$)
\item get $+1$ Plan (max $+2$)
\item get a new Techie move
\item get a new Techie move
\item get a second \linkmove{Technical Specialty}
% TODO \item get a 
\end{itemize}