% Hikikomori Inspiration: Akira (Valvrave), Komori Kiri
\subsection{Hikikomori}
{\itshape What was that noise? Is someone there? Maybe if you're quiet
  enough, they'll think you're not in. You shun outside
  contact. Friends only ever let you down. To support yourself, here,
  with your own two hands is enough. Well, in addition to the food
  your nice older sibling leaves outside your door.

The gentle hum of the machinery, the moonlight streaming in through
the viewing port. This is the life. Solitude is not loneliness; that's
what the others don't understand. Always asking what's wrong. They'll
never understand you. Not like you do.}

\subsubsection{Look}
Choose one for each:

Tired Eyes, Calculating Eyes, Hair Over Eyes, or \_\_\_\_\_.

Scruffy Hair, Long Hair, Covered Hair, or \_\_\_\_\_.

Tracksuit, T-shirt and Jeans, Pyjamas, or \_\_\_\_\_.

\subsubsection{Stats}
Choose one set:
\begin{itemize}
\setlength\itemsep{0em}
\item Cool$+1$ Talk$-2$ Hard$-1$ Fast$+1$ Tech$+2$ Plan$+2$
\item Cool$-1$ Talk$+1$ Hard${=}0$ Fast${=}0$ Tech$+2$ Plan$+1$
\item Cool$+1$ Talk$-1$ Hard$+2$ Fast$-1$ Tech$+2$ Plan$-1$
\item Cool${=}0$ Talk${=}0$ Hard$-2$ Fast$+2$ Tech$+2$ Plan$+1$
\end{itemize}

\subsubsection{Philosophy}
Choose one:
\paragraph{Yin:} Wait out a calamity by hiding.
\paragraph{Yang:} Open up to somebody.

\subsubsection{Introductions}
At the start of the first session, or when a new character joins, go round for introductions.
When you introduce your character, answer the following questions out loud:
\begin{itemize}
\item What do you look like? What impression does that give?
\item What do people think you're like? What about after they talk to you for five minutes?
\item In what way is people's first impression of you wrong or not quite the full story?
\end{itemize}

Then ask at least one of the following of the other characters:
\begin{itemize}
\item "Which one of you is basically my guardian?" Whoever answers, offer that player 1-interest.
\end{itemize}
Tell the others $-1$-interest. You tend to make others uncomfortable.

After each other character's introduction:
\begin{itemize}
\item Choose one and tell them "I think you're the coolest." Your interest in them is 2 regardless of what they offer you.
\item You prefer to be alone. Your interest in the others is 1 less than whatever they offer you.
\end{itemize}

\subsubsection{Starting Moves}
You start with four moves from the ones below:

\move{Security Expert}{attempt to overcome network security}{Tech}
{choose three:}
{choose one:
\begin{itemize}
\item You learn something useful.
\item You disable something.
\item You plant false information.
\item Your intrusion is undetected. Otherwise, they know you were there but not what you did.
\end{itemize}}

\subsubsection{Trapper}
You've mastered the art of turning electrical devices into dangerous and useful traps.
Choose three traps from the list below. When you have time to build and a safe place,
dismantle an electronic device and produce one of each of the traps you chose. When you
build a trap, choose a trigger from the ones available for that trap. Timed traps go off
after a certain amount of time that you specify when you set it. Proximity traps go off
when someone approaches the trap, doesn't matter who. Static traps do not trigger,
their effects are always active once set.
\begin{itemize}
\item \textbf{Alarm} (timed, proximity)\hfill Produces a loud noise.
\item \textbf{Stun} (proximity) \hfill Shocks a person unconscious.
\item \textbf{Hazard} (static) \hfill Makes a chokepoint, like a doorway, impassable.
\item \textbf{Paralysis} (proximity) \hfill Stops a person or group from moving.
\item \textbf{Incendiary} (timed) \hfill Starts a fire.
\item \textbf{Poison} (proximity) \hfill Delivers a slow-acting but lethal poison.
\item \textbf{Bomb} (timed, proximity) \hfill Causes an explosion.
\item \textbf{Camera} (static) \hfill Allows you to remotely observe the area.
\end{itemize}

\move{Frequent Poster}{put out word about something you want or need}{Tech if you post on the Internet, or Talk if you ask around}{Someone has it, just for you.}{You'll have to settle for something close or it comes with strings attached, your call.}

% move to Romantic
% \movedesc{Killer Rabbit}{act innocent}{roll+Plan on your \linkmove{Fast Talk} move instead of +Talk}

%\move{Doe-Eyed}{act innocent}{Plan}
%{Choose 2:
%\begin{itemize}
%\item Those nearby seek to protect you unless you give them a reason not to.
%\item 
%\end{itemize}

\move{Background Check}{research a person}{Tech if you use the web, or Talk if you ask around}{ask the GM 3 questions from the list:}{ask 1:
\begin{itemize}
\item Whom do they serve?
\item Where are they now?
\item What are they famous for?
\item How are they weak to me?
\item How can I get them to \_\_\_?
\end{itemize}}

\subsubsection{Killer Rabbit}
You seem totally unthreatening. People let their guard down around you and never consider you a danger until you give them a reason to.

%\movedesc{Viper Strike}{attack a surprised or defenseless enemy}{you can choose to deal your damage or roll+Fast}
%\rollres{You knock them out or kill them, your choice.}{as 10+, but choose 1:
%\begin{itemize}
%\item They fight back.
%\item They make a noise.
%\end{itemize}}

\movedesc{Spread the Word}{post about your recent exploits online}
{roll...
\begin{itemize}
\item +1 if you recently defeated a notable foe.
\item +1 if you recently publicised some major intrigue.
\item +1 if you recently acquired an important item.
\end{itemize}}
\rollres{choose 2,}{choose 1:
\begin{itemize}
\item An important figure wants to meet with you.
\item You hear of an opportunity.
\item Choose a location. The people there idolise you.
\item You don't draw unwanted attention to yourself.
\end{itemize}}

\subsubsection{Equipment}

You get:
\begin{itemize}
\item A concealable weapon for disproportionate self-defense. A hand taser or a kitchen knife, perhaps.
\item A heavily customised laptop
\item An item which affords you emotional security.
\end{itemize}

\subsubsection{Improvement}
\begin{itemize}
\item get $+1$ Cool (max $+2$)
\item get $+1$ Talk (max $+2$)
\item get $+1$ Hard (max $+2$)
\item get $+1$ Fast (max $+2$)
\item get $+1$ Tech (max $+3$)
\item get $+1$ Plan (max $+2$)
\item get a new Hikikomori move
\item get a new Hikikomori move
\item get a Techie move
\item get a Bodyguard and \linkmove{Command}
\end{itemize}