% Assassin Inspiration: Agent 47
\subsection{Assassin}
{\itshape For what reason do you do this? Don't bother lying to me,
  everyone has a reason. People may fight trivially, but they always
  kill for a cause. Be that a higher power or ideology, the sweet
  taste of revenge, or just the undeniable allure of filthy lucre.

You have as myriad methods of killing as you have targets. The
partygoing billionaire may warrant a .50 cal bullet to the brain from
the roof of an adjacent building, but the paranoid mob boss will
require a more\ldots intimate approach. Do you feel pleasure as the
garotte denies vital oxygen to his lungs? Did this man bring untold
suffering to countless innocents? Or was he just on the wrong side of
a million-dollar transaction?}

\subsubsection{Look}
Choose one for each:

Dead Eyes, Calculating Eyes, or Hard Eyes.

Shorn Hair, Slick Hair, or Hooded

Fatigues, Formal Wear, or Concealing Wear

\subsubsection{Stats}
Choose one set:
\begin{itemize}
\setlength\itemsep{0em}
\item Cool$+1$ Talk${=}0$ Hard$+1$ Fast${=}0$ Tech$-1$ Plan$+2$
\item Cool${=}0$ Talk$+1$ Hard${=}0$ Fast$+1$ Tech$-1$ Plan$+2$
\item Cool$+1$ Talk$-2$ Hard$-1$ Fast$+2$ Tech$+1$ Plan$+2$
\item Cool$+2$ Talk$-1$ Hard$-1$ Fast$-1$ Tech$+1$ Plan$+2$
\end{itemize}

Your Max Health and Max Load are both 7+Hard.

\subsubsection{Philosophy}
Choose one:
\paragraph{Yin:} Kill someone without anyone else knowing.
\paragraph{Yang:} Kill someone nobody will mourn.

\subsubsection{Introductions}
At the start of the first session, or when a new character joins, go round for introductions.
When you introduce your character, answer the following questions out loud:
\begin{itemize}
\item What do you look like? What impression does that give?
\item What do people think you're like? What about after they talk to you for five minutes?
\item In what way is people's first impression of you wrong or not quite the full story?
\end{itemize}

Then ask at least one of the following of the other characters:
\begin{itemize}
\item "Which one of you have I worked with before?" Whoever answers, offer that player 1-interest.
\item "Which one of you have I saved while I was just doing my job?" Whoever answers, offer that player 1-interest.
\end{itemize}
Tell the others $-1$-interest. You don't like giving away more details than necessary.

After each other character's introduction:
\begin{itemize}
\item Choose one and tell them "I don't trust you." Your interest in them is 1 more than whatever they offer you.
\item Your interest in the others is whatever they offer you.
\end{itemize}

\subsubsection{Starting Moves}
You start with four moves from the ones below:

\movedesc{Assassinate}{take time to make a plan to kill someone}{Name the person you want to kill. Ask the GM these questions. You and your allies take +1 forward when acting on the answers.
\begin{itemize}
\item What is their most powerful defense?
\item Who will avenge them?
\item Who else wants them dead?
\item What is my best opportunity?
\end{itemize}}

\movedesc{Silent Takedown}{when you have an unaware or defenseless enemy at close range or closer}{you can kill them without a sound, you don't need to use a weapon. Snap their neck if you have to.}

\movedesc{Disguise}{have time and materials} you can create a disguise that
will fool anyone into thinking you're someone else. Your actions can give you away but your
appearance won't.

\move{Visions of Death}{go into battle}{Plan}
{name one person who'll die and one who'll live.}
{name one person who'll die OR one person who'll live.
Don't name a player's character; name NPCs only.
The GM will make your vision come true, if it's even remotely possible.}

\movedesc{Overwatch}{watch over your allies from a vantage point}{roll+Plan for your \linkmove{Lookout} move instead of +Fast.}

\move{Death's Shadow}{stealth your way through a guarded area}{Plan}
{you're in.}
{you're in, but choose 1:
\begin{itemize}
\item Someone's on your tail.
\item You have to leave something behind.
\end{itemize}}

\subsubsection{Equipment}

You have your trusty sniper rifle (3-harm, far, single, loud, hi-tech, 2 weight). Choose 2 attachments:
\begin{itemize}
\item Silencer ($-$loud)
\item ACOG scope (+close)
\item .50 cal ammo (ignores armour, messy)
\item Bipod (+distant)
\item Magazine feed ($-$single, +semi-auto)
\end{itemize}

You also pick one of the following sidearms:
\begin{itemize}
\item Silenced 9mm (2-harm, hand, close, semi-auto, 1 weight)
\item Sawn-off Shotgun (3-harm, close, loud, 2 weight)
\end{itemize}

You get:
\begin{itemize}
\item Butterfly knife (3-harm, intimate, 0 weight)
\item Garrote wire
\item Leather gloves
\item 1 Explosives Kit (1 weight)
\end{itemize}

\subsubsection{Improvement}
\begin{itemize}
\item get $+1$ Cool (max $+2$)
\item get $+1$ Talk (max $+2$)
\item get $+1$ Hard (max $+2$)
\item get $+1$ Fast (max $+2$)
\item get $+1$ Tech (max $+2$)
\item get $+1$ Plan (max $+3$)
\item get a new Assassin move
\item get a new Assassin move
\item get an Agency, \linkmove{Mission}, and \linkmove{Call For Support}
\item get a Tactician move
\end{itemize}