% Swordsmaster Inspiration: Raiden, Mitsurugi
% TODO Decide whether to focus on samurai or general swordplay
\subsection{Swordsmaster}
{\itshape These fools lack honour and discipline. Look at them now,
  laughing carelessly over a shared lunch. They could be attacked
  right this minute, and only you would be able to defend
  yourself. While they waste away their time you sit here, tirelessly
  drawing and resheathing your sword to shave off those precious
  milliseconds that could mean the difference between life and death.

A warrior's life is tough, to be sure, but it has its rewards. What
are they to you? To lay down your life in defense of your lord, like
the samurai of old? Or do you prefer to feel the breath of your enemy
leave them, while you bask in the knowledge that when it came right
down to it, you were better than them? Whatever your goal, you will
find it hard to attain with these weaklings around. They lack honour
and discipline, yes, but you can change that.}

\subsubsection{Look}

Choose one for each:

Tired Eyes, Fierce Eyes, or Piercing Eyes.

Topknot, Wild Hair, or Shorn Hair

Gi and Hakama, Smart Clothes, or Bandages

\subsubsection{Stats}
Choose one set:
\begin{itemize}
\setlength\itemsep{0em}
\item Cool$+1$ Talk$-1$ Hard$+1$ Fast$+2$ Tech$-1$ Plan$+1$
\item Cool$+1$ Talk$+1$ Hard$+1$ Fast$+2$ Tech$-1$ Plan$-1$
\item Cool${=}0$ Talk$-1$ Hard$+2$ Fast$+2$ Tech$-1$ Plan$-1$
\item Cool$+1$ Talk$-1$ Hard${=}0$ Fast$+2$ Tech$+1$ Plan${=}0$
\end{itemize}

Your Max Health and Max Load are both 8+Hard.

\subsubsection{Philosophy}
Choose one:
\paragraph{Yin:} Defeat a worthy opponent.
\paragraph{Yang:} Fight for a good cause.

\subsubsection{Introductions}
At the start of the first session, or when a new character joins, go round for introductions.
When you introduce your character, answer the following questions out loud:
\begin{itemize}
\item What do you look like? What impression does that give?
\item What do people think you're like? What about after they talk to you for five minutes?
\item In what way is people's first impression of you wrong or not quite the full story?
\end{itemize}

Then ask at least one of the following of the other characters:
\begin{itemize}
\item "Which one of you beat me in a fair fight?" Whoever answers, offer that player 1-interest.
\item "Which one of you humiliated me?" Whoever answers, offer that player $-1$-interest.
\end{itemize}
Tell the others $-1$-interest. You're a bit of an eccentric.

After each other character's introduction:
\begin{itemize}
\item Choose one and tell them "I think you're the weakest." Your interest in them is 1 more than whatever they offer you.
\item You have no time for frivolities with the others. Your interest in them is 1 less than whatever they offer you.
\end{itemize}

\subsubsection{Starting Moves}
You start with \linkmove{Signature Weapon}, plus three moves from the ones below:

\subsubsection{Signature Weapon}\label{sec:Signature Weapon}
You are the bone of your sword. Perhaps it was created by a master smith centuries ago, or perhaps you found it on the floor. Regardless, this is your sword and it is irreplaceable, so don't lose it.

Your base sword comes with a matching sheath and is (2-harm, hand, 2 weight).

Choose a look:
\begin{itemize}
\item Straight or Curved
\item Single-edged, Double-edged, or Thrusting
\item Simple Design, Elaborate Design, or High-Tech Design
\end{itemize}

Choose two enhancements:
\begin{itemize}
\item Serrated ($+1$-harm)
\item Vibrating ($+1$ piercing, messy, hi-tech)
\item Disposable (infinite)
\item Perfectly-Balanced (precise)
\item Tasseled (+short, thrown)
\item Well-Crafted ($-1$ weight)
\item Twin (you have two and can dual-wield, but each individually is 1-harm and 1 weight. You can deal damage with both during an attack, but your other enhancement applies to only one blade)
\end{itemize}

\move{Quickdraw}{are attacked in melee by an enemy while your sword is sheathed}{Fast}
{draw your sword and inflict your damage, negating the incoming attack}
{draw your sword and inflict your damage, but the enemy's attack still lands}

\move{You Are Already Dead}{resheathe your sword immediately after dealing damage}{Cool}
{Choose 2:
\begin{itemize}
\item Additional wounds are revealed on your enemy, adding 1-harm to the damage and applying the messy tag.
\item Your spirit overflows, hitting nearby enemies for 1s-harm
\item You terrify or impress onlookers.
\end{itemize}}
{choose 1}

% TODO why do they ask a question if you study them from afar?
\move{Battlefield Psychology}{study an opponent in battle}{Cool}
{ask their player any one question. They must answer truthfully.}
{As $10+$, but they get to ask you a question as well. Tell them the truth, now.}

\subsubsection {Move 5 Placeholder} % TODO

\subsubsection {Move 6 Placeholder} % TODO

\subsubsection{Equipment}
You get your signature weapon, but choose your defenses:
\begin{itemize}
\item Padded Clothes (1-armour, 1 weight)
\item Samurai Armour (2-armour, 3 weight)
\item Exoskeleton (2-armour, fused, 0 weight)
\end{itemize}

\subsubsection{Improvement}
\begin{itemize}
\item get $+1$ Cool (max $+2$)
\item get $+1$ Talk (max $+2$)
\item get $+1$ Hard (max $+2$)
\item get $+1$ Fast (max $+3$)
\item get $+1$ Tech (max $+2$)
\item get $+1$ Plan (max $+2$)
\item get a new Swordsmaster move
\item get a new Swordsmaster move
\item get an Agency, \linkmove{Mission}, and \linkmove{Call For Support}
% TODO \item get a Bodyguard and \linkmove{Command}
\end{itemize}