% Martial Artist Inspiration: Bruce Lee, Avatar tLA
\subsection{Martial Artist}
{\itshape Your comrades are weak. Sure, they may be hotshots with
  their guns, gadgets, or even their fists, but they each have a
  weakness, and to a skilled warrior like you, a man is only as strong
  as his weaknesses.

100 push-ups. 200 sit-ups. 50 laps. Then, when that's done, you can
remove the iron weights from your limbs. After that, it's off to your
teacher for sparring practice. Will he be impressed with your spirit,
as befitting his top student? Or do your reasons for studying worry
him, and with good reason?}
\subsubsection{Look}
Choose one for each:

Determined Eyes, Calm Eyes, or Eager Eyes

Shaved Head, Flowing Hair, or Neat Hair

Training Clothes, Casual Clothes, or Formal Clothes

\subsubsection{Stats}
Choose one set:
\begin{itemize}
\setlength\itemsep{0em}
\item Cool${=}0$ Talk$+1$ Hard$+1$ Fast$+2$ Tech${=}0$ Plan$-1$
\item Cool$+2$ Talk$-1$ Hard${=}0$ Fast$+2$ Tech$-1$ Plan${=}0$
\item Cool$+1$ Talk$+2$ Hard$+1$ Fast$+2$ Tech$-2$ Plan$-1$
\item Cool$-1$ Talk${=}0$ Hard$+2$ Fast$+2$ Tech$-1$ Plan${=}0$
\end{itemize}

Your Max Health and Max Load are both 8+Hard.

\subsubsection{Philosophy}
Choose one:
\paragraph{Yin:} Kill a defenseless or surrendered enemy.
\paragraph{Yang:} Help someone else grow.

\subsubsection{Introductions}
At the start of the first session, or when a new character joins, go round for introductions.
When you introduce your character, answer the following questions out loud:
\begin{itemize}
\item What do you look like? What impression does that give?
\item What do people think you're like? What about after they talk to you for five minutes?
\item In what way is people's first impression of you wrong or not quite the full story?
\end{itemize}

Then ask at least one of the following of the other characters:
\begin{itemize}
\item "Which one of you trains with me?" Whoever answers, offer that player 1-interest.
\item "Which one of you insulted my school?" Whoever answers, offer that player $-1$-interest.
\end{itemize}
Tell the others 0-interest.

After each other character's introduction:
\begin{itemize}
\item Choose one and tell them "I want to impress you." Your interest in them is 1 more than whatever they offer you.
\item Your interest in the others is whatever they offer you.
\end{itemize}

\subsubsection{Starting Moves}
You start with \linkmove{Fighting Style}, plus three moves from the others below:

% For Martial Artist, maybe focus more on a code of ethics,
% possibly using precepts from the Cleric's Deity
% or consider merging with swordsmaster

\subsubsection{Fighting Style}
You were trained in some ancient style of martial arts. Give your style a name.
Using your fighting style counts as wielding a weapon: (2-harm, intimate, fused, two-handed, 0 weight).

Choose 2 from the list below:
\begin{itemize}
\item Your style trained you for fighting armoured foes. $+2$ piercing.
\item Your style focuses on disarming foes. When you deal damage to an enemy, name one item they're holding. They drop it.
\item Your style relies on speed to overwhelm your foes. +precise.
\item Your style emphasises the importance of protecting others. When you \linkmove{Lookout}, hold $+1$, even on a $6-$.
\item Your style requires great discipline to master. When you \linkmove{Persevere}, take +1 forward.
\end{itemize}

Choose 1 from the list below:
\begin{itemize}
\item A rival has sworn to destroy you.
\item Your master has turned his back on you.
\item Your school's arts are forbidden and dangerous.
\end{itemize}

%\move{Focus}{concentrate your energy into your fists}{Hard}{Hold 3}{Hold 1}
%Spend your hold when you make an unarmed attack to choose one of the following enhancements for that attack:
%\begin{itemize}
%\item Your energy resonates through armour. Gain $+1$ piercing.
%\item Your energy increases the impact of your fists. Gain the precise tag.
%\item Immediately close the distance between you and a target in close range.
%\end{itemize}

\move{Ancestral Spirits}{meditate and consult those who came before you for guidance}{Cool}
{The spirits give you clear advice. Take +1 forward when following it.}
{The spirits give you vague or conflicting advice.}
Either way, the spirits may ask you a question in return. (You don't have to tell them the truth)

\move{Fleet of Foot}{run across a surface that cannot hold your weight}{Fast}
{you make it across gracefully and without trouble.}
{you make it across, but expose yourself to danger somehow. The GM will tell you how.}

\subsubsection{Move 4 Placeholder} % TODO

\subsubsection{Move 5 Placeholder} % TODO

\subsubsection{Move 6 Placeholder} % TODO

\subsubsection{Equipment}

You get:
\begin{itemize}
\item 1 First Aid Kit (1 weight)
\end{itemize}

\subsubsection{Improvement}
\begin{itemize}
\item get $+1$ Cool (max $+2$)
\item get $+1$ Talk (max $+2$)
\item get $+1$ Hard (max $+2$)
\item get $+1$ Fast (max $+3$)
\item get $+1$ Tech (max $+2$)
\item get $+1$ Plan (max $+2$)
\item get a new Martial Artist move
\item get a new Martial Artist move
% TODO \item get 
\item get a Bodyguard and \linkmove{Command}.
\end{itemize}