\subsection{Disciple}
{\itshape
% TODO
}

\subsubsection{Look}
Choose one for each or write your own:

Determined Eyes, Bored Eyes, Eager Eyes, or \_\_\_\_\_.

Wild Hair, Neat Hair, Shorn Hair, or \_\_\_\_\_.

Training Clothes, Casual Clothes, Formal Clothes, or \_\_\_\_\_.

\subsubsection{Stats}
% TODO

\subsubsection{Philosophy}
Choose one:
\paragraph{Yin:} Defeat a worthy opponent.
\paragraph{Yang:} Put yourself in harm's way.

\subsubsection{Introductions}
At the start of the first session, or when a new character joins, go round for introductions.
When you introduce your character, answer the following questions out loud:
\begin{itemize}
\item What do you look like? What impression does that give?
\item What do people think you're like? What about after they talk to you for five minutes?
\item In what way is people's first impression of you wrong or not quite the full story?
\end{itemize}

Then ask the following of one of the other characters:
\begin{itemize}
\item "Which one of you have I fought?" Whoever answers, offer that player 1-interest.
\end{itemize}
Tell the others 0-interest.

After each other character's introduction:
\begin{itemize}
\item Choose one and tell them "I think you're the weakest." Your interest in them is 2 regardless of what they offer you.
\item Choose one and tell them "I want to impress you." Your interest in them is 1 more than whatever they offer you.
\end{itemize}

\subsubsection{Starting Moves}

\subsubsection{Oath}
You have sworn to train your body and mind to perfection. Choose an Oath:
\begin{itemize}
\item To never let anyone humiliate you again. When you suffer harm, suffer 1 less harm.
\item To never let your friends come to harm. When a nearby ally would suffer harm, you can impose yourself and suffer the harm instead.
\item To become a force to be reckoned with. When you inflict harm, inflict 1 more harm.
\end{itemize}

\move{Battlefield Psychology}{put someone's combat skills to the test without harming them}{Cool}
{ask their player any one question. They must answer truthfully.}
{As $10+$, but they get to ask you a question as well. Tell them the truth, now.}

\movedesc{Full Force}{succeed a Brawl with a 10+}{you may choose both options.}

\subsubsection{Equipment}

Choose one:
\begin{itemize}
\item Training Weapon
\item Training Gloves
\end{itemize}