% Brawler Inspirations: Heavy, AW Gunlugger, Yamada (Valvrave)
\subsection{Brawler}
{\itshape They always say weapons don't kill people, people do. Well,
  what are the weapons for, then? A weapon is nothing without a strong
  body wielding it. Look at the others. They think their pop-guns and
  glorified tree branches will protect them in a fight. Maybe, but
  where will they be when those weapons are taken away?

They call you names sometimes. ``Meathead'', they say. ``Numbskull'',
``Shit-For-Brains''. They laugh. Well, they'll be laughing on the
other side of their faces one day. When the enemy has them jailed, and
they see you removing the bars one by one like so many toothpicks. Or
maybe you'll just crush one of their skulls like a watermelon. Nobody
will be laughing then.}

\subsubsection{Look}
Choose one for each:

Wild Eyes, Determined Eyes, or Bored Eyes

Shorn Hair, Wild Hair, or Mask

Sporty Gear, Outdoor Gear, or Remnants of Experimentation

\subsubsection{Stats}
Choose one set:
\begin{itemize}
\setlength\itemsep{0em}
\item Cool$+2$ Talk${=}0$ Hard$+2$ Fast$+1$ Tech$-2$ Plan${=}0$
\item Cool$+1$ Talk$+1$ Hard$+2$ Fast$+1$ Tech$-1$ Plan$-1$
\item Cool$-1$ Talk$-1$ Hard$+2$ Fast$+2$ Tech$+1$ Plan$-1$
\item Cool$+1$ Talk$+1$ Hard$+2$ Fast$+1$ Tech$+1$ Plan$-2$
\end{itemize}

Your Max Health and Max Load are both 10+Hard.

\subsubsection{Philosophy}
Choose one:
\paragraph{Yin:} Make a mess of somebody.
\paragraph{Yang:} Put yourself in harm's way.

\subsubsection{Introductions}
At the start of the first session, or when a new character joins, go round for introductions.
When you introduce your character, answer the following questions out loud:
\begin{itemize}
\item What do you look like? What impression does that give?
\item What do people think you're like? What about after they talk to you for five minutes?
\item In what way is people's first impression of you wrong or not quite the full story?
\end{itemize}

Then ask at least one of the following of the other characters:
\begin{itemize}
\item "Which one of you have I fought?" Whoever answers, offer that player 1-interest.
\item "Which one of you clearly thinks I'm an idiot?" Whoever answers, offer that player $-1$-interest.
\end{itemize}
Tell the others 1-interest. You're just not a complicated person.

After each other character's introduction:
\begin{itemize}
\item Choose one and tell them "I think you're the prettiest." Your interest in them is 2 regardless of what they offer you.
\item You have trouble expressing yourself to the others. Your interest in them is 1 less than whatever they offer you.
\end{itemize}

\subsubsection{Starting Moves}
You start with \linkmove{My Guns Are Right Here}, plus three moves from the others below:

\subsubsection{My Guns Are Right Here}\label{sec:My Guns Are Right Here}
Your unarmed strike counts as a weapon: (2-harm, intimate, fused, 0 weight).

\movedesc{Full Force}{succeed a Brawl with a 10+}{you may choose both options.}

\move{Like Shell of Egg}{intimidate information out of an enemy with a show of force}{Hard}
{they immediately tell you what you want to know. What you do next is up to you.}
{they agree to tell if you let them go, and want to be certain they won't be harmed.}

\movedesc{Battle-Hardened}{persevere or go on lookout}{roll+Hard instead of what that move requires}

\movedesc{Relentless}{inflict harm}{inflict $+1$-harm}

\move{The Hard Way}{use straight-up force to destroy an inanimate obstacle}{Hard}{choose 3.}{choose 2.}
\begin{itemize}
\item It doesn’t take a very long time
\item Nothing of value is damaged
\item It doesn’t make an inordinate amount of noise
\item You can fix the thing again without a lot of effort
\end{itemize}

\subsubsection{Equipment}
You have your fists, but I guess you can also have a gun, you know, just to be on the safe side. Choose one:
\begin{itemize}
\item Hunting Shotgun (3-harm, semi-auto, loud, messy, close, 2 weight)
\item Grenade Launcher (4-harm, semi-auto, loud, messy, close, area, 3 weight)
\item Rocket Launcher (4-harm, single, loud, messy, close, far, area, 3 weight)
\end{itemize}

You get:
\begin{itemize}
\item 2 Stimpaks (0 weight)
\end{itemize}

\subsubsection{Improvement}
\begin{itemize}
\item get $+1$ Cool (max $+2$)
\item get $+1$ Talk (max $+2$)
\item get $+1$ Hard (max $+3$)
\item get $+1$ Fast (max $+2$)
\item get $+1$ Tech (max $+2$)
\item get $+1$ Plan (max $+2$)
\item get a new Brawler move
\item get a new Brawler move
\item get a Swordsmaster move
\item get an Assassin move
\end{itemize}