% Champion Inspiration: Kamina, Compa
\subsection{Champion}

{\itshape What do the people of Mecha World do when they're lying
  face-down in the dirt? When their dreams are shattered by cruelty,
  and when all hope turns to despair, to whom do they turn? They need
  someone to show that all is not lost, that fighting back is still
  possible. They need someone to show that if you cut them, they
  \emph{will} bleed. They need someone like you.

Nothing is impossible. You will make your friends understand that. You
will prove it. Whatever they say your chances are, if you keep your
chin up, and inspire others to do the same, you can overcome any
obstacle. That's what you believe, right? Let's put it to the test.}

\subsubsection{Look}
Choose one for each:

Determined Eyes, Friendly Eyes, or Relaxed Eyes

Wild Hair, Tidy Hair, or Bandana

Casual Clothes, Revealing Clothes, or Military Dress

\subsubsection{Stats}
Choose one set:
\begin{itemize}
\setlength\itemsep{0em}
\item Cool$+2$ Talk$+1$ Hard$+1$ Fast$+1$ Tech$-2$ Plan$+1$
\item Cool$+2$ Talk$+2$ Hard$-1$ Fast$-1$ Tech$-1$ Plan$+1$
\item Cool$+2$ Talk$+1$ Hard${=}0$ Fast$+1$ Tech${=}0$ Plan$-1$
\item Cool$+2$ Talk${=}0$ Hard$+2$ Fast${=}0$ Tech$-1$ Plan$-1$
\end{itemize}

Your Max Health and Max Load are both 8+Hard.

\subsubsection{Philosophy}
Choose one:
\paragraph{Yin:} Demoralise enemies by defeating their leader.
\paragraph{Yang:} Endanger yourself to protect someone weaker than you.

\subsubsection{Introductions}
At the start of the first session, or when a new character joins, go round for introductions.
When you introduce your character, answer the following questions out loud:
\begin{itemize}
\item What do you look like? What impression does that give?
\item What do people think you're like? What about after they talk to you for five minutes?
\item In what way is people's first impression of you wrong or not quite the full story?
\end{itemize}

Then ask the following of one the other characters:
\begin{itemize}
\item "Which one of you is always relying on me?" Whoever answers, offer that player 1-interest.
\end{itemize}
Tell the others 0-interest.

After each other character's introduction:
\begin{itemize}
\item Choose one and tell them "I feel like you need the most support." Your interest in them is 1 more than whatever they offer you.
\item You'll always listen to your comrades. Your interest in the others is 1 more than whatever they offer you.
\end{itemize}

\subsubsection{Starting Moves}
You start with four moves from the ones below:

\movedesc{Inspire}{lead the attack against a foe}{those you lead take +1 forward and +2 armour forward.}

\movedesc{Pep Talk}{give advice to another player's character}
{tell that player what you think they should do. They get +1 forward
when following your advice and you each mark experience if they do.}
           
\subsubsection{Do The Impossible}
At the start of the session, hold 1.
Spend your hold when a player misses a roll to treat that roll as a 10+ instead.

\movedesc{If It Bleeds}{deal damage}{choose an ally, that ally gets +1 forward and +1-harm forward against your target}

\move{Mano a Mano}{issue a challenge to a single enemy}{Talk}
{They attack only you, and only they attack you.}
{Choose one: They attack only you, or only they attack you.}

\movedesc{Caretaker}{watch over a friend}{you may roll+ your interest in them rather than +Fast}

\subsubsection{Equipment}
You have:
\begin{itemize}
\item A medical kit.
\item A worn but cherished photograph of \_\_\_\_\_.
\end{itemize}

\subsubsection{Improvement}
\begin{itemize}
\item get $+1$ Cool (max $+3$)
\item get $+1$ Talk (max $+2$)
\item get $+1$ Hard (max $+2$)
\item get $+1$ Fast (max $+2$)
\item get $+1$ Tech (max $+2$)
\item get $+1$ Plan (max $+2$)
\item get a new Paragon move
\item get a new Paragon move
\item get a move from any class
\item get a move from any class
\end{itemize}