% needs rethinking
% Experiment Inspiration:
\subsection{Experiment}
{\itshape What \emph{are} you? Out of which fiery pit did you crawl?
  And for what reason were you cursed with that terrible insight that
  no man has ever seen before or since? At what point did you first
  take that glimpse into the true nature of the world?  Whatever you
  saw, it consumed you, until barely a shell remained.

That was when they found you. With technology, they gave you the
physical and mental strength to deal with your curse. They made you
strong. And when it was done, I wonder, did you say your farewells
amicably, or do their severed limbs now litter the destroyed and
burning facility where you made your reintroduction upon the world?}

\subsubsection{Look}
Choose one for each:

Dead Eyes, Mad Eyes, or Covered Eyes

Flowing Hair, Bald, or Concealing Headwear

Tattered Clothes, Restrictive Clothes, or Ceremonial Garb

\subsubsection{Stats}
Choose one set:
\begin{itemize}
\setlength\itemsep{0em}
\item Cool${=}0$ Talk$-1$ Hard$+2$ Fast$-1$ Tech$+2$ Plan${=}0$
\item Cool$+1$ Talk${=}0$ Hard$+2$ Fast$-1$ Tech$+1$ Plan${=}0$
\item Cool$+1$ Talk$-2$ Hard$+2$ Fast$+1$ Tech$+1$ Plan$+1$
\item Cool${=}0$ Talk$-1$ Hard$+2$ Fast$+1$ Tech${=}0$ Plan$+1$
\end{itemize}

Your Max Health and Max Load are both 10+Hard.

\subsubsection{Philosophy}
Choose one:
\paragraph{Yin:} Cause an agonising death.
\paragraph{Yang:} Use your powers constructively.

\subsubsection{Introductions}
At the start of the first session, or when a new character joins, go round for introductions.
When you introduce your character, answer the following questions out loud:
\begin{itemize}
\item What do you look like? What impression does that give?
\item What do people think you're like? What about after they talk to you for five minutes?
\item In what way is people's first impression of you wrong or not quite the full story?
\end{itemize}

Then ask at least one of the following of the other characters:
\begin{itemize}
\item "Which one of you was party to the experiments?" Whoever answers, offer that player 1-interest.
\item "Which one of you has seen me lose control?" Whoever answers, offer that player $-1$-interest.
\end{itemize}
Tell the others $-1$-interest. You keep yourself secret.

After each other character's introduction:
\begin{itemize}
\item Your interests are unpredictable and inscrutible. Your interest in them is 1 more or 1 less than whatever they offer you, your call.
\end{itemize}

\subsubsection{Starting Moves}
You start with \linkmove{Elemental Savant}, plus three moves from the others below:

\subsubsection{Elemental Savant}\label{sec:Elemental Savant}
You've always seen more than other people, but thanks to your technological enhancements, you can now commune with the spirit of a certain element. Choose one:
\begin{itemize}
\item The Flirtatious Mistress of the Cleansing Fire
\item The Furious Lawmaker of the Crackling Lightning
\item The Patient Survivor of the Inhospitable Cold
\item The Avericious Savage of the Debilitating Corrosion
\end{itemize}
The Spirit may be capricious, but they have your best interests at heart. You can call upon them for advice, but they may not directly meddle in mortal affairs.

\move{An Acquired Taste}{endure an effect or element which falls under your spirit's domain}{Hard}{your spirit protects you and you suffer no ill effects}{the effect or harm is reduced}

\move{Elementary}{let your spirit's power flow through you to accomplish a task}{Tech}{choose two:}{choose one:
\begin{itemize}
  \item The effect you desire comes to pass
  \item You retain control.
  \item You avoid paying your spirit's price.
  \end{itemize}
}

\subsubsection {Move 4 Placeholder} % TODO

\subsubsection {Move 5 Placeholder} % TODO

\subsubsection {Move 6 Placeholder} % TODO

\subsubsection{Equipment}
You have a prototype rifle that spews your element (2-harm, close, loud, full-auto, two-handed, 3 weight) + an appropriate elemental tag.

Choose your defenses:
\begin{itemize}
\item Armoured Plating (1 armour, 1 weight), 2 Tech Items (2 weight)
\item Full Plate (2 armour, 3 weight)
\end{itemize}

You get:
\begin{itemize}
\item 2 Stimpaks (0 weight)
\end{itemize}

\subsubsection{Mecha Signature Weapon}
Your mecha's weapon depends on your chosen spirit:
\paragraph{Fire:} Flamethrower (3-harm, close, full-auto, fire, two-handed, 3 weight)
\paragraph{Lightning:} EMP Cannon (3s-harm, close, single, emp, two-handed, 3 weight)
\paragraph{Cold:} Cryo Beam (1-harm, 2s-harm, close, full-auto, two-handed, 3 weight)
\paragraph{Corrosion:} Acid Launcher (2-harm, 1s-harm, close, semi-auto, two-handed, 3 weight)

\subsubsection{Improvement}
\begin{itemize}
\item get $+1$ Cool (max $+2$)
\item get $+1$ Talk (max $+2$)
\item get $+1$ Hard (max $+3$)
\item get $+1$ Fast (max $+2$)
\item get $+1$ Tech (max $+2$)
\item get $+1$ Plan (max $+2$)
\item get a new Experiment move
\item get a new Experiment move
\item get an Agency, \linkmove{Mission}, and \linkmove{Call For Support}
\item get a Brawler move
\end{itemize}