\subsection{Celebrity}
{\itshape
% TODO
}

\subsubsection{Look}
Choose one for each or write your own:

Detached Eyes, Cheerful Eyes, Curious Eyes, or \_\_\_\_\_.

Neat Hair, Glorious Hair, Flashy Hair, or \_\_\_\_\_.

Formal Dress, Revealing Clothes, Unwieldy Costume, or \_\_\_\_\_.

\subsubsection{Stats}
% TODO

\subsubsection{Philosophy}
Choose one:
\paragraph{Yin:} Spend your resources wastefully.
\paragraph{Yang:} Help the less privilaged.

\subsubsection{Introductions}
At the start of the first session, or when a new character joins, go round for introductions.
When you introduce your character, answer the following questions out loud:
\begin{itemize}
\item What do you look like? What impression does that give?
\item What do people think you're like? What about after they talk to you for five minutes?
\item In what way is people's first impression of you wrong or not quite the full story?
\end{itemize}

Then ask the following of the other characters:
\begin{itemize}
\item "" Whoever answers, offer that player 1-interest.
\end{itemize}
Tell the others 0-interest.

After each other character's introduction:
\begin{itemize}
\item Choose one and tell them "I find your way of living quite quaint." Your interest in them is 1 more than whatever they offer you.
\item Choose one and tell them "" Your interest in them is 1 more than whatever they offer you.
\end{itemize}

\subsubsection{Starting Moves}

\subsubsection{Entourage}
You command the respect of your underlings. Choose one:
\begin{itemize}
\item A near-superhuman bodyguard, who acts solely to protect you.
\item A couple of knowledgable advisers.
\item A flock of adoring fans, eager to do your bidding.
\end{itemize}