% Wiseguy Inspirations: Hazuma
\subsection{Wiseguy}
{\itshape Where would these misfits be without you, eh? Just the other
  day you tried to strike up a rousing conversation with the Brawler,
  and he \emph{hissed} at you. Hissed! Like a cat! No, no, no, these
  guys would be mincemeat by now if you weren't around to smooth
  things over.

Leave the deal-brokering, the negotiations, and the sweet-talking to
you. You'll always be around to talk your way out of a sticky
situation. No need to thank you, it's all part of the service. Well,
unless they're armed, in which case your former friends are on their
own!}
\subsubsection{Look}
Choose one for each:

Shifty Eyes, Sharp Eyes, or Gleeful Eyes

Tidy Hair, Slick Hair, or Ponytail

Concealing Clothes, Business Wear, or Snazzy Clothes

\subsubsection{Stats}
Choose one set:
\begin{itemize}
\setlength\itemsep{0em}
\item Cool$+1$ Talk$+2$ Hard$-1$ Fast${=}0$ Tech${=}0$ Plan$+1$
\item Cool${=}0$ Talk$+2$ Hard$-1$ Fast$+1$ Tech$+1$ Plan${=}0$
\item Cool$-1$ Talk$+2$ Hard$-2$ Fast$+2$ Tech$+1$ Plan$+1$
\item Cool${=}0$ Talk$+2$ Hard$-1$ Fast$-1$ Tech${=}0$ Plan$+2$
\end{itemize}

Your Max Health and Max Load are both 6+Hard.

\subsubsection{Philosophy}
Choose one:
\paragraph{Yin:} Uncover dirt on someone.
\paragraph{Yang:} Resolve a heated situation without violence.

\subsubsection{Introductions}
At the start of the first session, or when a new character joins, go round for introductions.
When you introduce your character, answer the following questions out loud:
\begin{itemize}
\item What do you look like? What impression does that give?
\item What do people think you're like? What about after they talk to you for five minutes?
\item In what way is people's first impression of you wrong or not quite the full story?
\end{itemize}

Then ask at least one of the following of the other characters:
\begin{itemize}
\item "Which one of you got me out of a pinch?" Whoever answers, offer that player 1-interest.
\item "Which one of you set me up and let me take the fall?" Whoever answers, offer that player $-1$-interest.
\end{itemize}
Tell the others 1-interest. You're an open person.

After each other character's introduction:
\begin{itemize}
\item Choose one and tell them "I have some dirt on you." Your interest in them is 2 regardless of what they offer you.
\item You've done your research on the others. Your interest in them is 1 greater than whatever they offer you.
\end{itemize}

\subsubsection{Starting Moves}
You start with four moves from the ones below:

% written by Luke
\move{Networking}{arrive at a new location and mention an old accomplice or contact}{Talk, describe how you remember them, and recount a whacky anecdote about them}
{they're in town, and owe you a favour or their life (take $+1$ ongoing to interacting with them until you're even)}
{they were living here at least recently, at the GM's discretion maybe they're still here; at the very least the trail will be hot. However, things have changed since the good old days---pick 1:
\begin{itemize}
\item They've changed.
\item You've changed.
\item They don't remember you, at least not fondly.
\item You still owe them a favour or money
\end{itemize}}

\move{Wisecrack}{tell a joke to defuse a tense situation}{Talk}
{Everyone present relaxes and becomes a little more amicable}
{Your joke falls flat, but the attempt causes everyone to calm down. Everyone becomes more amicable, but you take $-1$ forward, in shame.}

\move{Eye On The Door}{are in too deep and need a way out}{Plan, naming your escape route:}
{you're gone. Catch you later, suckers!}
{you can stay or go, but if you go you either leave something behind, or take something with you, the GM will tell you what.}

\move{Taunt}{insult or make a snarky comment at someone}{Talk}
{choose two:}
{choose one:
\begin{itemize}
\item you provoke them into making an error
\item you provoke them into revealing information
\item you don't provoke a retaliation
\end{itemize}}

\movedesc{A Real Charmer}{speak frankly with someone}{Ask their player a question from the list. They must answer truthfully. Their player will then pick a question to ask you. Tell them the truth, now.
\begin{itemize}
\item How is your character really feeling?
\item What does your character want to do?
\item What does your character want me to do?
\item How can I get your character to \_\_\_?
\end{itemize}}

\movedesc{Hold on to Your Hat}{give up on doing anything except avoiding harm}{gain +2 armour forward}

\subsubsection{Equipment}
You have your trusty piece(s) for when things go hot. Choose 1 and give it a nickname:
\begin{itemize}
\item Gold DE .50 AE (2-harm, 1 piercing, hand, close, semi-auto, valuable, 2 weight)
\item Dual Mini-Uzis (2-harm, two-handed, hand, close, full-auto, 1 weight) 
\end{itemize}

\subsubsection{Improvement}
\begin{itemize}
\item get $+1$ Cool (max $+2$)
\item get $+1$ Talk (max $+3$)
\item get $+1$ Fast (max $+2$)
\item get $+1$ Tech (max $+2$)
\item get $+1$ Plan (max $+2$)
\item get a new Wiseguy move
\item get a move from any class
\item get an Agency, \linkmove{Mission}, and \linkmove{Call For Support}
\item get \linkmove{Background Check}
\end{itemize}